A meta-analysis of mental rotation ability in the first years of life

### 2022-04-18 code/analysis.Rmd
Update multilevel model formulas

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ group | article,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)

@@

```{r, brms, echo=TRUE}
# Specify priors
priors <- c(
  prior(normal(0, 1), class = "Intercept"),
  prior(exponential(1), class = "sd")
)

# Run Bayesian multilevel model
res_brm <- brm(
  yi | se(sei) ~ 1 + (1 | group / article),
  data = dat_r,
  prior = priors,
  cores = 4,
  chains = 4,
  iter = 2000,
  sample_prior = TRUE,
  save_pars = save_pars(all = TRUE)
)
summary(res_brm)

>>>>

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ 1 | article / group,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)

@@

```{r, brms, echo=TRUE}
# Specify priors
prior_c <- c(
  set_prior("normal(0, 1)", class = "Intercept"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run Bayesian multilevel model
res_brm <- brm(
  yi | se(sei) ~ 1 + (1 | article / group),
  data = dat_r,
  prior = prior_c,
  cores = 4,
  chains = 4,
  iter = 2000,
  sample_prior = TRUE,
  save_pars = save_pars(all = TRUE)
)
summary(res_brm)
